\documentclass{article}
\usepackage{fullpage}
\usepackage{sectsty}
\usepackage{color}
\usepackage{enumerate}
\usepackage{graphicx, subfigure}
\usepackage{amsfonts, amsmath, amsthm, bm, amssymb}

\usepackage{macro}
\usepackage[utf8]{inputenc}
\usepackage[normalem]{ulem}
\usepackage{lipsum} % for sample text
\usepackage{changepage} % for the adjustwidth environment
%\sectionfont{\large}
\usepackage{color}

\newcommand{\defeq}{\mathrel{\mathop:}=}
\newcommand\bigCI{\mathop{\underline{\raisebox{0pt}[0pt][1pt]{$\;||\;$}}}}
\newcommand{\bs}{\boldsymbol}
\newcommand{\mb}{\mathbf}

\newcommand{\h}{{\bf h}}
\newcommand{\w}{{\bf w}}
\newcommand{\z}{{\bf z}}
\newcommand{\y}{{\bf y}}
\newcommand{\tu}{{\bf t}}
\newcommand{\vu}{{\bf v}}
\newcommand{\x}{{\bf x}}
\newcommand{\capalpha}{{\bf \alpha}}
\begin{document}

\section*{10-701 Introduction to Machine Learning}
{\large \bf Homework 1} \hfill {\it Due Oct 2, 11:59 am}

\noindent\rule{\textwidth}{1pt}

\vspace{5ex}
\subsection*{Rules:}
\vspace{2ex}

\begin{enumerate}
\item Homework submission is done via CMU Autolab system. 
Please compile your writeup and code in a single pdf file and submit to  {\tt \href{https://autolab.cs.cmu.edu/courses/10701-f15}{https://autolab.cs.cmu.edu/courses/10701-f15}}. 
Please let us know asap if you have trouble accessing Autolab.

\item Like conference websites, repeated submission is allowed. 
So please feel free to refine your answers. 
We will only grade the latest version.

\item Autolab may allow submission after the deadline, note however it is because of the late day policy. Please see course website for policy on late submission. 

\item Please typeset your homework using appropriate software such as \LaTeX. 
We will not accept scanned copies of handwritten papers. 


\item You are allowed to collaborate on the homework, but you should write up your own solution and code. Please indicate your collaborators in your submission.

\end{enumerate}

\vspace{7ex}

\noindent\rule{\textwidth}{1pt}
\newpage

\input{mrinmaya1}
\input{yuntian}
\input{mrinmaya2}

%\bibliography{mybib}{}
%\bibliographystyle{plain}
\end{document}